Kung Faux Pandas \\ \large A tool for enabling data sharing in health care

### 2018-05-14 paper/main.tex
Auto Update from local Sharelatex

@@

%\author{Seth Russel  \& James King}
\author{
  James King \& Seth Russell\\
  Data Science to Patient Value (D2V)\\
  School of Medicine \\
  University of Colorado Anschutz Medical Campus\\
%  Aurora, CO\\
  \texttt{seth.russell@ucdenver.edu} \\
  \texttt{james.king@ucdenver.edu} \\ 
  }

@@

\begin{abstract}
A description of an end-to-end system for easily generating synthetic data which contains no Personal Health Information (PHI), allowing example data to be distributed for reproducibility testing and other purposes.

@@

@@

\section{Appendix: Legal References}
In the U.S., the primary law affecting health data privacy is the Health Insurance Portability and Accountability Act (\href{https://www.hhs.gov/hipaa/for-professionals/index.html}{HIPAA}).

>>>>

\usepackage{soul}           % added by seth - remove before submission, provides highlighting support

@@

\author{
  James King \& Seth Russell\\
  Data Science to Patient Value (D2V)\\
  School of Medicine \\
  University of Colorado Anschutz Medical Campus\\
  Aurora, CO\\
  \texttt{james.king@ucdenver.edu} \\
  \texttt{seth.russell@ucdenver.edu} \\
  }

@@

\begin{abstract}
\hl{to finish:} A description of an end-to-end system for easily generating synthetic data which contains no Personal Health Information (PHI), allowing example data to be distributed for reproducibility testing and other purposes.

@@

The unique contribution to the space of reproducible machine learning by this paper is a no-configuration required method for faux data creation from user generated queries.The faux data will resemble the original data set but can be used freely without compliance risk because it contains no Protected Health Information (PHI).  Furthermore, with this method it is possible for an investigator to perform hypothesis articulation, data cleaning, analysis, visualization, and documentation without the ever having access to the underlying PHI data.

@@

As machine learning results are highly data dependent, the barriers around sharing health data make it difficult or impossible for others to verify or reproduce results with novel machine learning methods in the health care domain (? cite recent difficult to reproduce examples such as Google FHIR paper, others?). In order to resolve the problem of data sharing, various methods for data synthesis and de-identification have been developed in other data domains that have been applied to health care. The use of privacy preserving techniques as methods to safely share health care or other data have a history of re-identification risk as detailed by Sweeney \cite{sweeney_2002}. Alternative techniques of synthetic data have been used to avoid the potential problem of re-identification. One early example by Gray et al. \cite{gray_quickly_1994} used pseudo-random generation techniques to populate large databases with synthetic data for performance evaluation. Subsequent advances in techniques have generated more realistic data based on observed and publicly reported statistics, such as with the Synthea system \cite{walonoski_synthea:_2018}, that generates an entire outpatient Electronic Health Record (EHR) based on population statistics.

While advances in both de-identification and synthesis of data have been impressive, still more progress needs to be made. Techniques such as Synthea that generate an entire EHR require significant computational power and model development of every disease state desired and may not have the level of specificity as found in an actual EHR due to rare or complex conditions. Other techniques based on actual health data such as described by Gal et al. \cite{gal_data_2014} provide for the complexities found in real health data by building off of the condensation algorithm \cite{aggarwal_static_2008} though use of k-means clustering, Principle Component Analysis, and independent data generation pipelines based on a specific outcome variable. While the method as depicted by Gal results in a use case specific synthetic data set, the manual intervention required to develop a synthetic data requires an ongoing effort between the data source and researchers needing access to data. In this paper we propose a method that allows the user of the data to identify what attributes they are interested in, does not require manual intervention or generation of synthetic data, and is modular so that as new techniques are developed the system could be updated to take advantage of them.

\section{Methods}

? James write this section ?

\section{Conclusion}

Basically need to put abstract here...

\section{Appendix: Legal References}

\hl{Where to put this? Probably don't want to waste any of our 4 pages with an appendix... Include this in body or not at all?}

In the U.S., the primary law affecting health data privacy is the Health Insurance Portability and Accountability Act (\href{https://www.hhs.gov/hipaa/for-professionals/index.html}{HIPAA}).
